Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-09 overhead-table.tex
nicer and nicer ...

\newcommand{\yes}{YES}

@@

	\begin{tabular}{rllrr}
		\toprule
		\bfseries Endpoint & \bfseries Dashboard & \bfseries Outliers & \bfseries Mean (ms) & \bfseries SD (ms) \\

@@

	    create\_default\_ex...     &    &	    &  76.0 & 22.4 \\ 
	    create\_default\_ex...     &  \yes &    & 313.6 & 43.2 \\
	    create\_default\_ex...     &  \yes &  \yes & 385.3 & 16.9 \\

@@

	\end{tabular}
	\caption{Descriptive statistics of the response times reported by running the benchmark}
	\label{tab:benchmark}

>>>>

\newcommand{\yes}{\checkmark}

@@

	\begin{tabular}{rllrr}
		\toprule
		\bfseries Endpoint & \bfseries Dash. & \bfseries All Out. & \bfseries Mean (ms) & \bfseries SD (ms) \\

@@

	    create\_default\_ex...     &    &	    &  276.0 & 22.4 \\ 
	    create\_default\_ex...     &  \yes &    & 313.6 & 43.2 \\
	    create\_default\_ex...     &  \yes &  \yes & 385.3 & 16.9 \\

@@

	\end{tabular}
	\caption{Response times for three endpoints run 500 times in three different conditions each. Dash. = with dashboard. All Out. = every call being considered an outlier}
	\label{tab:benchmark}

### 2018-04-09 overhead.tex
nicer and nicer ...

	\begin{enumerate}
		\item With the dashboard disabled
		\item With the dashboard enabled but with the outlier detection deactivated
		\item With the dashboard enabled and the outlier treshold set to zero. This helps us measure the time usually spent in an outlier.
	\end{enumerate}

\Fref{fig:bench} shows using violin plots the distribution of times resulting from running the benchmark for three different endpoints on a quad-core machine, with Intel Core i5-4590 processor, @ 3.30GHz, 8G of RAM and 240GB SSD disk drive.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{benchmark2.pdf}
	\caption{The distribution of response times when calling the three endpoints for 500 times in three conditions: no dashboard, dashboard but no outliers, dashboard and always outlier routine}
	\label{fig:bench}
\end{figure}

>>>>

	\begin{enumerate}
		\item With no dashboard installed
		\item With the dashboard enabled but with the outlier detection deactivated
		\item With the dashboard enabled and the outlier treshold set to zero, thus effectively treating every request {\em like it were an outlier}\footnote{This forces all the requests to be treated as outliers, and thus provides insight into this situation, which otherwise would be hard to generate}.
	\end{enumerate}

\Fref{fig:bench} and Table \ref{tab:benchmark} present with descriptive statistics and respectively violin plots the distribution of times resulting from running the benchmark for three different endpoints on a quad-core machine, with Intel Core i5-4590 processor, @ 3.30GHz, 8G of RAM and 240GB SSD disk drive.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{benchmark2.pdf}
	\caption{The distribution of response times when calling the three endpoints for 500 times in three conditions: no dashboard, dashboard but no outliers, dashboard and every request treated as an outlier}
	\label{fig:bench}
\end{figure}
